Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2020-12-31 submission/NatCom_cv_models.tex
figs updated
minor text added to CV

We examine the performance of the four quality metrics (Log Frobenius norm, Log Spectral norm, Weighted Alpha, and Log $\alpha$-Norm) applied to each of the VGG, ResNet, ResNet-1K, and DenseNet series.
Figure~\ref{fig:vgg-metrics} 
plots the four quality metrics versus reported test accuracies~\cite{pytorch},% 
\footnote{These test accuracies have been previously reported and made publicly-available by others.  We take them as given.  We do not attempt to reproduce/verify them, since we do not permit ourselves access to training/test data.}
as well as a basic linear regression line, for the VGG series.
All four metrics correlate quite well with reported Top1 accuracies, with smaller norms and smaller values of $\hat{\alpha}$ implying better generalization (i.e., greater accuracy, lower error). 
\michael{The following, text and numbers, will need to be updated once we finalize the figures/tables.}
The Log $\alpha$-Norm metric ($\log\Vert\mathbf{W}\Vert_{\alpha}^{\alpha}$) performs best (RMSE of $0.42$, $R^2$ of $XXX$, and Kendall-$\tau$ of $XXX$, see Table~\ref{table:cv-models}); and the Weighted Alpha metric ($\hat\alpha =\alpha\log\lambda_{max} $) performs second best (RMSE of $0.48$, $R^2$ of $XXX$, and Kendall-$\tau$ of $XXX$, see Table~\ref{table:cv-models}).
\michael{Put comment on why these three metrics, that HT-SR says that $\hat{\alpha}$ should exhibit good linear correlation, and a few comments on non-normality to address R1 concerns.}

\begin{figure}[t]
    \centering
    \subfigure[Log Frobenius Norm, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_log_norm_accs.png}
        \label{fig:vgg-fnorm}
    }
    \qquad
    \subfigure[Log Spectral Norm, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_log_spectral_norm_accs.png}
        \label{fig:vgg-snorm}
    }
    \qquad
    \subfigure[ Weighted Alpha, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_alpha_weighted_accs.png}
        \label{fig:vgg-walpha}
    }
    \qquad
    \subfigure[Log $\alpha$-Norm, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_log_alpha_norm_accs.png}
        \label{fig:vgg-pnorm}
    }
    \caption{Comparison of Average Log Norm and Weighted Alpha quality metrics versus reported test accuracy for pretrained VGG models: 
             VGG11, VGG13, VGG16, and VGG19, with and without Batch Normalization (BN),
             trained on ImageNet, available in pyTorch (v1.4).  
             Metrics fit by linear regression, RMSE reported.  }
    \label{fig:vgg-metrics}
\end{figure}

@@

    \subfigure[ ResNet, Log $\alpha$-Norm ]{
        \includegraphics[width=4.9cm]{img/ResNet_logpnorm_accs.png}
        \label{fig:resnet-accuracy}
    }
    \qquad
    \subfigure[ ResNet-1K, Log $\alpha$-Norm ]{
        \includegraphics[width=4.9cm]{img/ResNet-1K_log_alpha_norm_accs.png}
        \label{fig:resnet1k-accuracy}
    }
    \caption{Comparison of Average $\alpha$-Norm quality metric versus reported Top1 test accuracy for the ResNet and ResNet-1K pretrained (pyTorch) models. 
             \michael{FROM V1: Symbols and text are way to small on these and other figures; axes/ticks way too small; need different symbols, not just red versus green; etc.}
            }
    \label{fig:cv2-accuracy}
\end{figure}

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|c|}
\hline
 Series                      & \#                    & Metric         & $\langle\log\Vert\mathbf{W}\Vert_{F}\rangle$ & $\langle\log\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
\multirow{3}{4em}{VGG}       & \multirow{3}{1em}{6}  & RMSE           & 0.56 & 0.53 & 0.48          & \textbf{0.42}  \\
                             &                       & $R^2$          &  XXX &  XXX &  XXX          &  XXX           \\
                             &                       & Kendall-$\tau$ &  XXX &  XXX &  XXX          &  XXX           \\
\hline
\multirow{3}{4em}{ResNet}    & \multirow{3}{1em}{5}  & RMSE           &  0.9 & 1.4  & \textbf{0.61} & 0.66           \\
                             &                       & $R^2$          &  XXX &  XXX &  XXX          &  XXX           \\
                             &                       & Kendall-$\tau$ &  XXX &  XXX &  XXX          &  XXX           \\
\hline
\multirow{3}{4em}{ResNet-1K} & \multirow{3}{1em}{19} & RMSE           &  2.4 & 3.6  & \textbf{1.8}  & 1.9            \\
                             &                       & $R^2$          &  XXX &  XXX &  XXX          &  XXX           \\
                             &                       & Kendall-$\tau$ &  XXX &  XXX &  XXX          &  XXX           \\
\hline
\multirow{3}{4em}{DenseNet}  & \multirow{3}{1em}{4}  & RMSE           &  0.3 & 0.26 & \textbf{0.16} & 0.21           \\
                             &                       & $R^2$          &  XXX &  XXX &  XXX          &  XXX           \\
                             &                       & Kendall-$\tau$ &  XXX &  XXX &  XXX          &  XXX           \\
\hline
\end{tabular}
\end{center}
\caption{Quality metrics 
         (RMSE, smaller is better; $R^2$, XXX is better; and Kendall-$\tau$ rank correlation, XXX is better)
         for reported Top1 test error for pretrained models in each architecture series.  
         Column \# refers to number of models.  
         VGG, ResNet, and DenseNet were pretrained on ImageNet.  
         ResNet-1K was pretrained on ImageNet-1K. 
}
\label{table:cv-models}
\end{table}

>>>>

We examine the performance of the four quality metrics (Log Frobenius norm, Log Spectral norm, Weighted Alpha, and Log $\alpha$-Norm) applied to each of the VGG, ResNet, ResNet-1K, and DenseNet series.
Figure~\ref{fig:vgg-metrics} 
plots the four quality metrics versus reported test accuracies~\cite{pytorch},% 
\footnote{These test accuracies have been previously reported and made publicly-available by others.  We take them as given.  We do not attempt to reproduce/verify them, since we do not permit ourselves access to training/test data.}
as well as a basic linear regression line, for the VGG series.
All four metrics correlate quite well with reported Top1 accuracies, with smaller norms and smaller values of $\hat{\alpha}$ implying better generalization (i.e., greater accuracy, lower error). 
\michael{The following, text and numbers, will need to be updated once we finalize the figures/tables.}
The Log $\alpha$-Norm metric ($\log\Vert\mathbf{W}\Vert_{\alpha}^{\alpha}$) performs best (RMSE of $0.42$, $R^2$ of $XXX$, and Kendall-$\tau$ of $XXX$, see Table~\ref{table:cv-models}); and the Weighted Alpha metric ($\hat\alpha =\alpha\log\lambda_{max} $) performs second best (RMSE of $0.48$, $R^2$ of $XXX$, and Kendall-$\tau$ of $XXX$, see Table~\ref{table:cv-models}).
\michael{Put comment on why these three metrics, that HT-SR says that $\hat{\alpha}$ should exhibit good linear correlation, and a few comments on non-normality to address R1 concerns.}
\charles{The Log Spectral Norm metric correlates very well with small, simpler data sets like the VGG and DenseNet architectures, however, when moving to the larger and more complex ResNet series, the PL-based metrics Log $\alpha$-Norm ($\log\Vert\mathbf{W}\Vert_{\alpha}^{\alpha}$) 
and  Weighted Alpha ($\hat\alpha =\alpha\log\lambda_{max} $) metrics perform better across all measures.}

\begin{figure}[t]
    \centering
    \subfigure[Log Frobenius Norm, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_log_norm_accs.png}
        \label{fig:vgg-fnorm}
    }
    \qquad
    \subfigure[Log Spectral Norm, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_log_spectral_norm_accs.png}
        \label{fig:vgg-snorm}
    }
    \qquad
    \subfigure[ Weighted Alpha, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_alpha_weighted_accs.png}
        \label{fig:vgg-walpha}
    }
    \qquad
    \subfigure[Log $\alpha$-Norm, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_log_alpha_norm_accs.png}
        \label{fig:vgg-pnorm}
    }
    \caption{Comparison of Average Log Norm and Weighted Alpha quality metrics versus reported test accuracy for pretrained VGG models: 
             VGG11, VGG13, VGG16, and VGG19, with and without Batch Normalization (BN),
             trained on ImageNet, available in pyTorch (v1.4).  
             Metrics fit by linear regression, RMSE, R2, and the Kendal-tau rank correlation metric reported.  }
    \label{fig:vgg-metrics}
\end{figure}

@@

    \subfigure[ ResNet, Log $\alpha$-Norm ]{
        \includegraphics[width=4.9cm]{img/ResNet_log_alpha_norm_accs.png}
        \label{fig:resnet-accuracy}
    }
    \qquad
    \subfigure[ ResNet-1K, Log $\alpha$-Norm ]{
        \includegraphics[width=4.9cm]{img/ResNet-1K_log_alpha_norm_accs.png}
        \label{fig:resnet1k-accuracy}
    }
    \caption{Comparison of Average $\alpha$-Norm quality metric versus reported Top1 test accuracy for the ResNet and ResNet-1K pretrained (pyTorch) models. 
             \michael{FROM V1: Symbols and text are way to small on these and other figures; axes/ticks way too small; need different symbols, not just red versus green; etc.}
\charles{See changes}
            }
    \label{fig:cv2-accuracy}
\end{figure}

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|c|}
\hline
 Series                      & \#                    & Metric         & $\langle\log\Vert\mathbf{W}\Vert^{2}_{F}\rangle$ & $\langle\log\Vert\mathbf{W}\Vert^{2}_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
\multirow{3}{4em}{VGG}       & \multirow{3}{1em}{6}  & RMSE           & 0.56 & \textbf{0.23} & 0.48          & 0.34  \\
                             &                       & $R^2$          & 0.88 & \textbf{0.98} &  0.92         &  0.96           \\
                             &                       & Kendall-$\tau$ & -0.79 &  \textbf{-0.93} & \textbf{-0.93} & \textbf{-0.93}        \\
\hline
\multirow{3}{4em}{ResNet}    & \multirow{3}{1em}{5}  & RMSE           &  0.9 & 0.97 & \textbf{0.61} & 0.66        \\
                             &                       & $R^2$          &  0.92 &  0.9 &  \textbf{0.96}   &  0.9         \\
                             &                       & Kendall-$\tau$ &  -1.0 &  -1.0 &  -1.0          &  -1.0        \\
\hline
\multirow{3}{4em}{ResNet-1K} & \multirow{3}{1em}{19} & RMSE           &  2.4 & 2.8  & \textbf{1.8}  & 1.9          \\
                             &                       & $R^2$          &  0.81 &  0.74 &  \textbf{0.89}    &  0.88           \\
                             &                       & Kendall-$\tau$ &  -0.79 &  -0.79 &  \textbf{-0.89}  &  -0.88           \\
\hline
\multirow{3}{4em}{DenseNet}  & \multirow{3}{1em}{4}  & RMSE           &  0.3 & \textbf{0.11}  & 0.16 & 0.21       \\
                             &                       & $R^2$          &  0.93 &  \textbf{0.99} &  0.98      &  0.97    \\
                             &                       & Kendall-$\tau$ &  -1.0 &  -1.0 &  -1.0         &  -1.0     \\
\hline
\end{tabular}
\end{center}
\caption{Quality metrics 
         (RMSE, smaller is better; $R^2$, XXX is better; and Kendall-$\tau$ rank correlation, XXX is better)
         for reported Top1 test error for pretrained models in each architecture series.  
         Column \# refers to number of models.  
         VGG, ResNet, and DenseNet were pretrained on ImageNet.  
         ResNet-1K was pretrained on ImageNet-1K. 
}
\label{table:cv-models}
\end{table}
